---
title: "Kermit Perceptions/ Rank Based Tests"
author: "Lauren Jack"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

LBJ's first message in the document

Kermit says hi

"LBJ has changed name to "Github Seaweed Queen""

"lauraing has pivoted into oblivion" <- yes.

If you are the collaborator:
- load the tidyverse
- read in the kermit data as 'kermit'
- make some side-by-side histograms of the Score.pre for all respondents, separated by the Gender column

```{r}

library(tidyverse)
kermit <- read_csv("kermit.csv")

kermit_hist <- ggplot(kermit, aes(x = Score.pre)) +
  geom_histogram(bins = 4) +
  facet_wrap(~Gender)

kermit_hist

```

Creator: Perform ranked-based comparissons using Man-Whitney U abd Wilcoxin-Signed Rank

Question: Is there a significant difference in pretalk ranks of kermit for Male and Female respondents?

```{r}
mwu_kermit <- kermit %>% 
  wilcox.test(Score.pre ~ Gender, .)

# Null : There is not a significant difference in ranks for male and female respondents
# Alternative: There is a significant difference in ranks for male and female respondents

mwu_kermit
```

There was no significant difference in ranks between male and female respondents (W = 155.5, p = 0.04, alpha = 0.05)
